BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-08 evaluation.tex
Abstract Added

\section{Conclusions}
In this chapter we have outlined the results of BlueTracer's experimental evaluation. In order to assess BlueTracer's run-time overhead, we have tested it on a number of applications performing various tasks, employing a four different modes of operation. We have also introduced the overhead per event metric as a way of quantifying the run-time overhead introduced by BlueTracer. The results showed that the typical overhead per event is in the 4$\times10^{-5}$ - 22$\times10^{-5}$ seconds range.
Then we validated BlueTracer with Al-Khaser, an open-source application employed to assess how stealthy an analysis system is with respect to many evasion techniques used in the wild. BlueTracer was able to remain hidden to all the checks performed by Al-Khaser, thus proving to be effective at staying undetected. Furthermore, BlueTracer's tracking abilities also turned out to be efficacious, since evidence of a large portion of Al-Khaser's techniques could found in BlueTracer's log.

>>>>

\section{Conclusions}
In this chapter we have outlined the results of BlueTracer's experimental evaluation. In order to assess BlueTracer's run-time overhead, we have tested it on a number of applications performing various tasks, employing a four different modes of operation. We have also introduced the overhead per event metric as a way of quantifying the run-time overhead introduced by BlueTracer. The results showed that the typical overhead per event is in the 4$\times10^{-5}$ - 22$\times10^{-5}$ seconds range.
Then we validated BlueTracer with Al-Khaser, an open-source application employed to assess how stealthy an analysis system is with respect to many evasion techniques used in the wild. BlueTracer was able to remain hidden to all the checks performed by Al-Khaser, thus proving to be effective at staying undetected. Furthermore, BlueTracer's tracking abilities also turned out to be efficacious, since evidence of the vast majority of Al-Khaser's techniques was present in BlueTracer's log.

### 2018-07-08 introduction.tex
Abstract Added

A problem that nearly all dynamic analyses - including API hooking - have to face is adversarial behavior from \textit{evasive malware}, i.e., malware that active checks whether it is being executed in a hostile environment, such as a well-known sandbox solution for dynamic analysis. In that case, an evasive sample conceals its harmful behavior to avoid detection, for instance by executing an exit sequence. Evasive techniques are frequently adopted by modern malware. According to a March 2018 Symantec Internet Security Report, 18\% of recently observed new samples are aware of hardware virtualization solutions used also for malware analysis \cite{Symantec}. To make matters worse, most API hooking techniques proposed to date in literature are easily detectable by malware, and not coupled with mechanisms to hide their presence from evasive malware.

>>>>

A problem that nearly all dynamic analyses - including API hooking - have to face is adversarial behavior from \textit{evasive malware}, i.e., malware that actively checks whether it is being executed in a hostile environment, such as a well-known sandbox solution for dynamic analysis. In that case, an evasive sample conceals its harmful behavior to avoid detection, for instance by executing an exit sequence. Evasive techniques are frequently adopted by modern malware. According to a March 2018 Symantec Internet Security Report, 18\% of recently observed new samples are aware of hardware virtualization solutions used also for malware analysis \cite{Symantec}. To make matters worse, most API hooking techniques proposed to date in literature are easily detectable by malware, and not coupled with mechanisms to hide their presence from evasive malware.
